Fusion of Mass Spectrometry and Raman Spectroscopy Data

### 2024-05-07 dev/dev_paracetamol.Rmd
Small fixes normalization

ms$add_replicate_names(
  c(rep("fiz_1", 3),
    rep("fiz_2", 3),
    rep("fiz_3", 3),
    rep("set_32_1", 3),
    rep("set_32_2", 3),
    rep("set_32_3", 3),
    rep("set_33_1", 3),
    rep("set_33_2", 3),
    rep("set_33_3", 3),
    rep("fiz_caff_1", 3),
    rep("fiz_caff_2", 3),
    rep("fiz_caff_3", 3),
    rep("fiz_ass_1", 3),
    rep("fiz_ass_2", 3),
    rep("fiz_ass_3", 3),
    rep("fiz2_1", 3),
    rep("fiz2_2", 3),
    rep("fiz2_3", 3),
    rep("fiz_acid_1", 3),
    rep("fiz_acid_2", 3),
    rep("fiz_acid_3", 3),
    rep("ass_1", 3),
    rep("ass_2", 3),
    rep("ass_3", 3),
    rep("ass2_1", 3),
    rep("ass2_2", 3),
    rep("ass2_3", 3),
    rep("caff_1", 3),
    rep("caff_2", 3),
    rep("caff_3", 3),
    rep("par_1", 3),
    rep("par_2", 3),
    rep("par_3", 3),
    rep("blank", 23)
  )
)

@@

```{r}
ms <- ms$subset_analyses(analyses = c(1:9, 28:72, 82:99, 118:121))
ms$add_blank_names(rep("blank", 76))
ms$load_spectra()
```

@@

raman$add_replicate_names(
  c(
    rep("ass_1", 3),
    rep("ass_2", 3),
    rep("ass_3", 3),
    rep("caff_1", 3),
    rep("caff_2", 3),
    rep("caff_3", 3),
    rep("blank", 9),
    rep("fiz_1", 3),
    rep("fiz_2", 3),
    rep("fiz_3", 3),
    rep("fiz_ass_1", 3),
    rep("fiz_ass_2", 3),
    rep("fiz_ass_3", 3),
    rep("fiz_ass_b_2", 9),
    rep("fiz_caff_1", 3),
    rep("fiz_caff_2", 3),
    rep("fiz_caff_3", 3),
    rep("fiz_b", 9),
    rep("fiz2_1", 3),
    rep("fiz2_2", 3),
    rep("fiz2_3", 3),
    rep("fiz_d", 9),
    rep("background", 4),
    rep("fiz_acid_1", 3),
    rep("fiz_acid_2", 3),
    rep("fiz_acid_3", 3),
    rep("par_1", 3),
    rep("par_odd", 3),
    rep("par_3", 3),
    rep("par_2", 3),
    rep("cali_150_mgml", 9),
    rep("cali_010_mgml", 9),
    rep("cali_025_mgml", 9),
    rep("cali_050_mgml", 9),
    rep("cali_075_mgml", 9),
    rep("background", 4)
  )
)

@@

```{r}
raman <- raman$subset_analyses(analyses = c(1:45, 55:63, 73:81, 95:106, 110:115))
raman$add_blank_names(rep("blank", 81))
```

@@

```{r}
rSpec <- raman$get_spectra()
rSpec <- rSpec[order(rSpec$replicate), ]
mrSpec <- matrix(rSpec$intensity, nrow = length(unique(rSpec$replicate)), ncol = length(unique(rSpec$shift)), byrow = TRUE, dimnames = list(as.character(unique(rSpec$replicate)), as.character(unique(rSpec$shift))))

@@

attr(fusedMat, "xaxis.name") = "Keys"
attr(fusedMat, "xaxis.values") = seq_len(ncol(fusedMat))
```

@@

# Statistic analysis (via mdatools)

### PCA

```{r, include=FALSE}
library(mdatools)
data(people)

m = pca(people, 7, scale = TRUE, info = "People PCA model")
m = selectCompNum(m, 5)

print(m$res$cal)

par(mfrow = c(1, 2))
mdaplot(m$res$cal$scores, type = "p", show.labels = TRUE, show.lines = c(0, 0))
mdaplot(m$loadings, type = "p", show.labels = TRUE, show.lines = c(0, 0))
```

```{r}
fusedMat2 <- prep.autoscale(fusedMat, center = FALSE, scale = TRUE)
cl <- StreamFind:::.get_colors(rownames(fusedMat2))
fig <- plot_ly()
xVal <- seq_len(length(fusedMat2[1, ]))
for (i in seq_len(nrow(fusedMat2))) {
  fig <- fig %>% add_trace(
    x = xVal,
    y = fusedMat2[i, ],
    type = "scatter", mode = "lines",
    line = list(width = 0.5, color = unname(cl[i])),
    name = names(cl)[i],
    legendgroup = names(cl)[i],
    showlegend = TRUE
  )
}
xaxis <- list(
  linecolor = toRGB("black"),
  linewidth = 2, title = "Bins",
  titlefont = list(size = 12, color = "black")
)
yaxis <- list(
  linecolor = toRGB("black"),
  linewidth = 2, title = "Intensity",
  titlefont = list(size = 12, color = "black")
)
fig <- fig %>% plotly::layout(xaxis = xaxis, yaxis = yaxis)
fig
```

```{r, include=FALSE}

m = pca(fusedMat, 3, scale = FALSE, info = "People PCA model")
plot(m, show.labels = TRUE)
mdaplot(m$res$cal$scores, type = "p", show.labels = TRUE, show.lines = c(0, 0))

par(mfrow = c(2, 2))
plotVariance(m, type = "h", show.labels = TRUE)
plotQDoF(m)
plotT2DoF(m)
plotDistDoF(m)

par(mfrow = c(1, 2))
plotQDoF(m, main = "DoF plot (classic)")

m = setDistanceLimits(m, lim.type = "ddrobust")
plotQDoF(m, main = "DoF plot (robust)")

plotExtreme(m, comp = 1:2, main = "Extreme plot (cal)")

plotLoadings(m, 1:2, type = 'l')

# par(mfrow = c(2, 2))
# mdaplot(m$res$cal$scores, type = "p", show.labels = TRUE, show.lines = c(0, 0))
# mdaplot(m$loadings, type = "p", show.labels = TRUE, show.lines = c(0, 0))
# plotResiduals(m$res$cal, show.labels = TRUE)
# plotVariance(m$res$cal, type = "h", show.labels = TRUE, labels = "values")
```

```{r ,echo=FALSE,fig.width=10,fig.height=4}

library(plotly)

loadings_plot <- plot_ly()

loadings_plot <- loadings_plot %>% add_trace(
  x = m$loadings[rownames(m$loadings) %in% colnames(mrSpec), "Comp 1"],
  y = m$loadings[rownames(m$loadings) %in% colnames(mrSpec), "Comp 2"],
  type = "scatter",
  mode = "markers+text",
  text = rownames(m$loadings)[(rownames(m$loadings) %in% colnames(mrSpec))],
  textfont = list(size = 14),
  legendgroup = "Raman",
  name = "Raman",
  marker = list(size = 10)
)

loadings_plot <- loadings_plot %>% add_trace(
  x = m$loadings[rownames(m$loadings) %in% colnames(mmSpec), "Comp 1"],
  y = m$loadings[rownames(m$loadings) %in% colnames(mmSpec), "Comp 2"],
  type = "scatter",
  mode = "markers+text",
  text = rownames(m$loadings)[(rownames(m$loadings) %in% colnames(mmSpec))],
  textfont = list(size = 14),
  legendgroup = "MS",
  name = "MS",
  marker = list(size = 10, color = "red")
)

loadings_plot %>% layout(
    title = "PCA Loadings Plot",
    xaxis = list(title = "Principal Component 1"),
    yaxis = list(title = "Principal Component 2")
  )

```

### PLS

```{r}

library(mdatools)
data(people)

idx = seq(4, 32, 4)
Xc = people[-idx, -4]
yc = people[-idx, 4, drop = FALSE]
Xt = people[idx, -4]
yt = people[idx, 4, drop = FALSE]

m = pls(Xc, yc, 7, scale = TRUE, cv = 1, info = "Shoesize prediction model")

par(mfrow = c(2, 2))
plotRegcoeffs(m)
plotRegcoeffs(m, ncomp = 2)
plot(m$coeffs, ncomp = 3, type = "b", show.labels = TRUE)
plot(m$coeffs, ncomp = 2)

par(mfrow = c(1, 2))
plotPredictions(m)
plotPredictions(m, ncomp = 1)

plotVIPScores(m, show.labels = TRUE)

res = predict(m, Xt, yt)
print(res)

data(simdata)
Xc = simdata$spectra.c
yc = simdata$conc.c[, 1]
Xt = simdata$spectra.t
yt = simdata$conc.t[, 1]

m = pls(Xc, yc, 10, x.test = Xt, y.test = yt, ncomp.selcrit = "min")
summary(m)

plot(m)

```

### PLS-DA

```{r}
data(iris)

cal.ind = c(1:25, 51:75, 101:125)
val.ind = c(26:50, 76:100, 126:150)

Xc = iris[cal.ind, 1:4]
Xv = iris[val.ind, 1:4]

cc.all = iris[cal.ind, 5]
cv.all = iris[val.ind, 5]

cc.vir = cc.all == "virginica"
cv.vir = cv.all == "virginica"
show(cc.vir)

m.all = plsda(Xc, cc.all, 3, cv = 1)
m.vir = plsda(Xc, cc.vir, 3, cv = 1, classname = "virginica")

summary(m.all)

par(mfrow = c(1, 2))
plotPredictions(m.all)
plotPredictions(m.vir)

res = predict(m.all, Xv, cv.all)
summary(res)

par(mfrow = c(1, 1))
plotPredictions(res, show.labels = TRUE)

```

### SIMCA
```{r}
idx = seq(1, nrow(iris), by = 2)

# split the values
Xc = iris[idx, 1:4]
cc = iris[idx, 5]

Xt = iris[-idx, 1:4]
ct = iris[-idx, 5]
```

### MCR

```{r}

data(carbs)
m = mcrpure(carbs$D, ncomp = 3, offset = 0.10)
summary(m)

par(mfcol = c(2, 2))
plotContributions(m)
plotSpectra(m)
plotSpectra(m, comp = 2)
plotContributions(m, comp = 2)

S = prep.norm(mda.t(carbs$S), "length")
S.hat = prep.norm(mda.t(m$resspec), "length")

c = predict(m, mda.t(carbs$S))
c = c / apply(c, 2, sum)
show(c)
```

```{r}
m = mcrpure(fusedMat, ncomp = 2, offset = 0.10)
summary(m)

par(mfcol = c(2, 2))
plotContributions(m)
plotSpectra(m)
plotSpectra(m, comp = 1)
plotContributions(m, comp = 1)

par(mfcol = c(1, 2))
plotVariance(m)
plotCumVariance(m)

plotPuritySpectra(m, ylim = c(0, 1600))

```

## Other Methods

### PCA in base R

```{r , include=FALSE, fig.width=10,fig.height=5}
data_pca <- prcomp(fusedMat, center = TRUE, scale. = FALSE)
pcs <- data_pca$x
pc_data <- data.frame(PC1 = pcs[, 1], PC2 = pcs[, 2], Species = rownames(pcs))
pca_plot <- plot_ly(
  data = pc_data,
  x = ~PC1,
  y = ~PC2,
  type = "scatter",
  mode = "markers+text",
  text = ~Species,
  textfont = list(size = 14),
  marker = list(size = 12),
  textposition = "top center"
) %>%
  layout(
    title = "PCA Plot with Annotations",
    xaxis = list(title = "Principal Component 1"),
    yaxis = list(title = "Principal Component 2")
  )
pca_plot
```

```{r ,echo=FALSE,fig.width=10,fig.height=4}
loadings <- as.data.frame(data_pca$rotation[, 1:2])

loadings_plot <- plot_ly()

loadings_plot <- loadings_plot %>% add_trace(
  x = loadings[rownames(loadings) %in% colnames(mrSpec), "PC1"],
  y = loadings[rownames(loadings) %in% colnames(mrSpec), "PC2"],
  type = "scatter",
  mode = "markers+text",
  text = rownames(loadings)[(rownames(loadings) %in% colnames(mrSpec))],
  textfont = list(size = 14),
  legendgroup = "Raman",
  name = "Raman",
  marker = list(size = 10)
)

loadings_plot <- loadings_plot %>% add_trace(
  x = loadings[rownames(loadings) %in% colnames(mmSpec), "PC1"],
  y = loadings[rownames(loadings) %in% colnames(mmSpec), "PC2"],
  type = "scatter",
  mode = "markers+text",
  text = rownames(loadings)[(rownames(loadings) %in% colnames(mmSpec))],
  textfont = list(size = 14),
  legendgroup = "MS",
  name = "MS",
  marker = list(size = 10, color = "red")
)

loadings_plot %>% layout(
    title = "PCA Loadings Plot",
    xaxis = list(title = "Principal Component 1"),
    yaxis = list(title = "Principal Component 2")
  )

```

### Correlation Analysis

```{r}
# Calculate correlation matrix
correlation_matrix <- cor(fusedMat)

# Print correlation matrix
print(correlation_matrix)
```

### Distance Metrics

```{r}
# Calculate Euclidean distance matrix
distance_matrix <- dist(fusedMat)

# Print distance matrix
print(distance_matrix)
```

### Hierarchical Clustering

```{r}
# Perform hierarchical clustering
hc_result <- hclust(dist(fusedMat))

# Plot dendrogram
plot(hc_result)
```

### Multidimensional Scaling (MDS)

```{r}
# Calculate Euclidean distance matrix
distance_matrix <- dist(fusedMat)

# Perform MDS
mds_result <- cmdscale(distance_matrix)

# Plot MDS results
plot(mds_result[,1], mds_result[,2], pch = 19, col = "blue", xlab = "MDS1", ylab = "MDS2")

```

### Kernel Methods

```{r}
# Example code for kernel PCA (assuming Gaussian kernel)
library(kernlab)
kpca_result <- kpca(fusedMat, kernel = "rbfdot")

# Plot kernel PCA results
plot(kpca_result@pcv[,1], kpca_result@pcv[,2], pch = 19, col = "blue", xlab = "KPCA1", ylab = "KPCA2")
```

### Feature Selection and Importance

```{r}
# Example code for feature selection (using random forest as an example)
library(randomForest)
rf_model <- randomForest(fusedMat, importance = TRUE)
print(importance(rf_model))

var_importance <- importance(rf_model)
var_names <- rownames(var_importance)
var_scores <- var_importance[,"MeanDecreaseAccuracy"]  # Adjust column name as needed

# Sort variables by importance score
sorted_indices <- order(var_scores, decreasing = TRUE)
sorted_var_names <- var_names[sorted_indices]
sorted_var_scores <- var_scores[sorted_indices]

# Create bar plot
barplot(sorted_var_scores, names.arg = sorted_var_names, las = 2, cex.names = 0.8,
        main = "Variable Importance", xlab = "Variables", ylab = "Importance Score")
```

###  Cosine similarity and k-means clustering

```{r}
vectors <- fusedMat

similarity_matrix <- tcrossprod(vectors) / (sqrt(rowSums(vectors^2)) %*% t(sqrt(rowSums(vectors^2))))

# Perform k-means clustering
k <- 3  # Number of clusters
clusters <- kmeans(similarity_matrix, centers = k)

# Print cluster assignments
print(clusters$cluster)
```

### Similarity Measures

```{r}
vectors <- fusedMat

# Calculate cosine similarity between pairs of vectors
cosine_similarity <- function(x, y) {
  return(sum(x * y) / (sqrt(sum(x^2)) * sqrt(sum(y^2))))
}

similarity_matrix <- matrix(NA, nrow = nrow(vectors), ncol = nrow(vectors))
for (i in 1:nrow(vectors)) {
  for (j in 1:nrow(vectors)) {
    similarity_matrix[i, j] <- cosine_similarity(vectors[i,], vectors[j,])
  }
}

# Print similarity matrix
print(similarity_matrix)
```

### k-nearest neighbors (KNN) classification

```{r}
training_data <- fusedMat[c(1, 4), ]  # Replace this with your actual training data
test_data <- fusedMat[2:3, ]  # Replace this with your actual test data
labels <- rownames(fusedMat[c(1, 4), ])  # Replace this with your actual labels for training data

# Train KNN model
library(class)
knn_model <- knn(train = training_data, test = test_data, cl = labels, k = 3)

# Print predicted labels for test data
print(knn_model)
```

## Partial Least Squares (PLS)

Not applicable!

```{r}
# Example data
X <- fusedMat  # Replace this with your actual predictor variables
Y <- seq_len(nrow(fusedMat))  # Replace this with your actual response variable

# Perform PLS regression
library(pls)
pls_model <- plsr(Y ~ X, ncomp = 2)  # You can adjust the number of components (ncomp) as needed

# Predict using the PLS model
predicted_values <- predict(pls_model, newdata = X)

# Print predicted values
print(predicted_values)
```

## Support Vector Regression (SVR)

Not applicable!

```{r}
# Example data
X <- matrix(rnorm(100), nrow = 10)  # Replace this with your actual predictor variables
Y <- rnorm(10)  # Replace this with your actual response variable

# Train SVR model
library(e1071)
svr_model <- svm(Y ~ ., data = as.data.frame(X), kernel = "radial", epsilon = 0.1, cost = 1)  # Adjust parameters as needed

# Predict using the SVR model
predicted_values <- predict(svr_model, newdata = as.data.frame(X))

# Print predicted values
print(predicted_values)

```

## MCR-ALS (Multivariate Curve Resolution - Alternating Least Squares)

```{r}

# Perform MCR-ALS analysis
mcr_result <- mcr(fusedMat, nfac = 2)  # You can adjust the number of components (nfac) as needed

# Print MCR-ALS results
print(mcr_result)

```

>>>>

ms$add_replicate_names(
  c(rep("fiz1_1", 3),
    rep("fiz1_2", 3),
    rep("fiz1_3", 3),
    rep("fiz2_1", 3),
    rep("fiz2_2", 3),
    rep("fiz2_3", 3),
    rep("fiz3_1", 3),
    rep("fiz3_2", 3),
    rep("fiz3_3", 3),
    rep("fiz_caff_1", 3),
    rep("fiz_caff_2", 3),
    rep("fiz_caff_3", 3),
    rep("fiz_ass_1", 3),
    rep("fiz_ass_2", 3),
    rep("fiz_ass_3", 3),
    rep("fiz4_1", 3),
    rep("fiz4_2", 3),
    rep("fiz4_3", 3),
    rep("fiz_acid_1", 3),
    rep("fiz_acid_2", 3),
    rep("fiz_acid_3", 3),
    rep("ass_n_1", 3),
    rep("ass_n_2", 3),
    rep("ass_n_3", 3),
    rep("ass_1", 3),
    rep("ass_2", 3),
    rep("ass_3", 3),
    rep("caff_1", 3),
    rep("caff_2", 3),
    rep("caff_3", 3),
    rep("par_1", 3),
    rep("par_2", 3),
    rep("par_3", 3),
    rep("blank", 23)
  )
)

@@

```{r}
ms <- ms$subset_analyses(analyses = c(1:63, 73:99, 118:121))
ms$add_blank_names(rep("blank", 94))
ms$load_spectra()
```

@@

raman$add_replicate_names(
  c(
    rep("ass_1", 3),
    rep("ass_2", 3),
    rep("ass_3", 3),
    rep("caff_1", 3),
    rep("caff_2", 3),
    rep("caff_3", 3),
    rep("blank", 9),
    rep("fiz3_1", 3),
    rep("fiz3_2", 3),
    rep("fiz3_3", 3),
    rep("fiz_ass_n_1", 3),
    rep("fiz_ass_n_2", 3),
    rep("fiz_ass_n_3", 3),
    rep("fiz_ass_1", 3),
    rep("fiz_ass_2", 3),
    rep("fiz_ass_3", 3),
    rep("fiz_caff_1", 3),
    rep("fiz_caff_2", 3),
    rep("fiz_caff_3", 3),
    rep("fiz1_1", 3),
    rep("fiz1_2", 3),
    rep("fiz1_3", 3),
    rep("fiz4_1", 3),
    rep("fiz4_2", 3),
    rep("fiz4_3", 3),
    rep("fiz2_1", 3),
    rep("fiz2_2", 3),
    rep("fiz2_3", 3),
    rep("background", 4),
    rep("fiz_acid_1", 3),
    rep("fiz_acid_2", 3),
    rep("fiz_acid_3", 3),
    rep("par_1", 3),
    rep("par_odd", 3),
    rep("par_3", 3),
    rep("par_2", 3),
    rep("cali_150_mgml", 9),
    rep("cali_010_mgml", 9),
    rep("cali_025_mgml", 9),
    rep("cali_050_mgml", 9),
    rep("cali_075_mgml", 9),
    rep("background", 4)
  )
)

@@

```{r}
raman <- raman$subset_analyses(analyses = c(1:36, 46:90, 95:106, 110:115))
raman$add_blank_names(rep("blank", 99))
raman$plot_spectra(colorBy = "replicates")
```

@@

```{r}
rSpec <- raman$get_spectra()
rSpec <- rSpec[order(rSpec$replicate), ]
mrSpec <- matrix(rSpec$intensity, nrow = length(unique(rSpec$replicate)), ncol = length(unique(rSpec$shift)), byrow = TRUE, dimnames = list(as.character(unique(rSpec$replicate)), as.character(round(unique(rSpec$shift), digits = 1))))

@@

attr(fusedMat, "xaxis.name") = "Keys"
attr(fusedMat, "xaxis.values") = seq_len(ncol(fusedMat))

# Mean centering improves separation but can we do it?
library(mdatools)
fusedMat = prep.autoscale(fusedMat, center = TRUE, scale = FALSE)
```

@@

# Statistic analysis

## Overall PCA

```{r, include=FALSE}
library(mdatools)
m = pca(fusedMat, 3, center = FALSE, scale = FALSE, info = "Overall PCA model")
```

```{r ,echo=FALSE,fig.width=10,fig.height=4}
library(plotly)

cl <- StreamFind:::.get_colors(rownames(fusedMat))
scores_polt <- plot_ly()

scores_polt <- scores_polt %>% add_trace(
  x = m$res$cal$scores[, "Comp 1"],
  y = m$res$cal$scores[, "Comp 2"],
  type = "scatter",
  mode = "markers+text",
  color = names(cl),
  colors = cl,
  text = rownames(m$res$cal$scores),
  textfont = list(size = 14, color = cl),
  textposition = "top",
  marker = list(size = 10, color = cl),
  showlegend = FALSE
)

scores_polt <- scores_polt %>% layout(
  xaxis = list(title = "Principal Component 1"),
  yaxis = list(title = "Principal Component 2")
)

cl2 <- StreamFind:::.get_colors(1:2)
loadings_plot <- plot_ly()

loadings_plot <- loadings_plot %>% add_trace(
  x = m$loadings[rownames(m$loadings) %in% colnames(mrSpec), "Comp 1"],
  y = m$loadings[rownames(m$loadings) %in% colnames(mrSpec), "Comp 2"],
  type = "scatter",
  mode = "markers+text",
  text = rownames(m$loadings)[(rownames(m$loadings) %in% colnames(mrSpec))],
  textfont = list(size = 14, color = cl2[1]),
  textposition = "top",
  legendgroup = "Raman",
  name = "Raman",
  marker = list(size = 10, color = cl2[1])
)

loadings_plot <- loadings_plot %>% add_trace(
  x = m$loadings[rownames(m$loadings) %in% colnames(mmSpec), "Comp 1"],
  y = m$loadings[rownames(m$loadings) %in% colnames(mmSpec), "Comp 2"],
  type = "scatter",
  mode = "markers+text",
  text = rownames(m$loadings)[(rownames(m$loadings) %in% colnames(mmSpec))],
  textfont = list(size = 14, color = cl2[2]),
  textposition = "top",
  legendgroup = "MS",
  name = "MS",
  marker = list(size = 10, color = cl2[2])
)

loadings_plot <- loadings_plot %>% layout(
  xaxis = list(title = "Principal Component 1"),
  yaxis = list(title = "Principal Component 2")
)

subplot(
  scores_polt, loadings_plot, nrows = 1,
  shareX = FALSE, shareY = FALSE, titleX = TRUE, titleY = TRUE,
  margin = 0.1
)
```

## Unsupervised

Using Principle Components Analysis (PCA) for unsupervised evaluation.

```{r}
# rownames(fusedMat)
main_set <- fusedMat[c(14:15, 18), ]
test_set <- fusedMat[c(1:13, 16:17, 19:30), ]

m3 = pca(main_set, 2, center = FALSE, scale = FALSE, info = "Unsupervised PCA model", alpha = 1E-1, gamma = 1E-2)

plot(m3)

res = predict(m3, test_set)

c = categorize(m3, res)

names(c) <- rownames(test_set)

plotResiduals(m3, 
  res = list("train" = m3$res$cal, "new" = res),
  norm = TRUE, show.labels = TRUE,
  lim.col = c("red", "orange"), lim.lwd = c(2, 2), lim.lty = c(1, 2)
)

print(c)
```

## Supervised (classification)

Using k-nearest neighbors (KNN) for classification.

```{r}
train_set <- fusedMat[c(grep("_1", rownames(fusedMat)), grep("_2", rownames(fusedMat))), ]

train_set <- train_set[order(rownames(train_set)), ]

test_set <- fusedMat[grep("_3", rownames(fusedMat)), ]

labels <- factor(c(rep("ass", 2), rep("caff", 2), rep("fiz_acid", 2), rep("fiz_ass", 2), rep("fiz_caff", 2),
  rep("fiz_altered", 2), rep("fiz_altered", 2), rep("fiz", 2), rep("fiz", 2), rep("par", 2))
)

library(class)

knn_model <- knn(train = train_set, test = test_set, cl = labels, k = 3, prob = FALSE)

names(knn_model) <- rownames(test_set)

data.frame(class = knn_model)
# print(knn_model)
```

## Other

Using Hierarchical Clustering.

```{r}
hc_result <- hclust(dist(fusedMat), method = "ward.D2")
plot(hc_result)
```
